
```{r}
library(ggplot2)
```

1.Code for reading in the dataset and/or processing the data

```{r}
unzip("activity.zip")
df <- read.csv("activity.csv", header = T, sep = ',', stringsAsFactors = FALSE)
a <- summary(df)
print(a, type="html")
```

2. Histogram of the total number of steps taken each day

```{r, echo=TRUE}
step_perday <- aggregate(df$steps, by = list(df$date),sum, na.rm = T)
colnames(step_perday) <- c("date","steps")
b <- ggplot(data = step_perday, aes(x=step_perday$steps)) + geom_histogram(binwidth = 2000, fill = 'lightyellow', col = 'lightblue') 
print(b,type="html")
```

3. Mean and median number of steps taken each day

```{r}
datamean <- mean(step_perday$steps)
datamedian <- median(step_perday$steps)
print(datamean, type = "html")
print(datamedian, type="html")
```

4. Time series plot of the average number of steps taken
```{r}
step_int <- aggregate(df$steps, by=list(df$interval), mean, na.rm = T)
colnames(step_int) <- c("intervals","steps")
ggplot(data = step_int, aes(x=intervals, y=steps)) + geom_line(col = 'lightblue', size =1)
```

5. The 5-minute interval that, on average, contains the maximum number of steps
```{r}
step_int[which.max(step_int$steps),]
```

6. Code to describe and show a strategy for imputing missing data
```{r}
df2 = df
for(i in 1:nrow(df2)){
    if(is.na(df2$steps[i])){
        int = df2$interval[i]
        sub = subset(step_int, intervals == int)
        df2$steps[i] = sub$steps
    }
}
```

7. Histogram of the total number of steps taken each day after missing values are imputed
```{r}
step_int2 <- aggregate(df2$steps, by = list(df2$date), sum)
ggplot(data = step_int2, aes(x=step_int2$x)) + geom_histogram(binwidth = 2000, fill = 'blue', col = 'black')
```

8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
```{r}
df2$date = as.Date(df2$date)
df2$day = factor(format(df2$date, "%A"))
levels(df2$day) = list(weekday = c("Monday", "Tuesday","Wednesday", "Thursday", "Friday"), weekend = c("Saturday", "Sunday"))

we = subset(df2, df2$day == 'weekend')
step_int_we = aggregate(we$steps, by=list(we$interval), mean)
step_int_we$day = 'weekend'

wd = subset(df2, df2$day == 'weekday')
step_int_wd = aggregate(wd$steps, by=list(wd$interval), mean)
step_int_wd$day = 'weekday'

step_int_2 = rbind(step_int_we, step_int_wd)

colnames(step_int_2) <- c('interval', 'steps', 'day')

ggplot(data = step_int_2, aes(x = interval, y  = steps)) + facet_grid(day~.) + geom_line(col = 'steelblue', size = 1) + labs(x = 'Interval(5 minuts)', y = 'Average numeber of steps', title ='Time series plot(new)')
```



